Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-11 Manuscript/Manuscript.Rmd
.

```{r figure_3, echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
plots <- 1:4
for(i in 1:length(plots)){
  assign(paste0("p",plots[i]), cor_rug_plot(interesting_groups_low[i], "#3288bd"))
}

>>>>

```{r figure_3, echo=FALSE, fig.height=4, fig.width=7, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
plots <- 1:4
for(i in 1:length(plots)){
  assign(paste0("p",plots[i]), cor_rug_plot(interesting_groups_low[i], "#3288bd"))
}
